Rapid-response Bayesian sky localization for electromagnetic follow-up of gravitational-wave candidates

### 2013-02-12 ms.tex
Fixed typo

The second change of variables, from $\gamma$ and $gamma_\tau$ to $\gamma_\pm = \frac{1}{\sqrt{2}}(\gamma \pm \gamma_\tau)$, diagonalizes the Fisher matrix:
%
\begin{equation}
    \mathcal{I}'' = \bordermatrix{
        ~ & \rho & \gamma_+ & \gamma_- \cr
        \rho & 1 & 0 & 0 \cr
        \gamma_+ & 0 & \left(1 - \frac{\overline{\omega}}{\sqrt{\overline{\omega^2}}}\right)\rho^2 & 0 \cr
        \gamma_- & 0 & 0 & \left(1 + \frac{\overline{\omega}}{\sqrt{\overline{\omega^2}}}\right)\rho^2
    }.
\end{equation}
%
Thus, in the appopriate time units, the \textit{sum and difference} of the phase and time of the signal are measured independently.

>>>>

The second change of variables, from $\gamma$ and $\gamma_\tau$ to $\gamma_\pm = \frac{1}{\sqrt{2}}(\gamma \pm \gamma_\tau)$, diagonalizes the Fisher matrix:
%
\begin{equation}
    \mathcal{I}'' = \bordermatrix{
        ~ & \rho & \gamma_+ & \gamma_- \cr
        \rho & 1 & 0 & 0 \cr
        \gamma_+ & 0 & \left(1 - \frac{\overline{\omega}}{\sqrt{\overline{\omega^2}}}\right)\rho^2 & 0 \cr
        \gamma_- & 0 & 0 & \left(1 + \frac{\overline{\omega}}{\sqrt{\overline{\omega^2}}}\right)\rho^2
    }.
\end{equation}
%
Thus, in the appopriate time units, the \textit{sum and difference} of the phase and time of the signal are measured independently.
